### 2015-06-26 narrative/intro.tex
more questions

Our research into the storage system and middle ware layers must address many of these challenges including
\begin{enumerate}
\item  How do we describe the user intentions at the API layer and have this communicated down to the middle-ware and storage layers?
\item How do we allow users to define their user defined compression techniques and have this data read back from the storage system layers? Where do we execute the decompression techniques
\item How do we evaluate the tradeoffs at runtime to guide data placement, including the movement of data across the network, across the
different storage tiers? 
\item Can we use different forms of learning techniques as daemons on the system to perform data migration from one storage tier to another?
For example, if we see that a user is looking at one time slice after another for a certain object in their dataset which is in the slower tiers of 
the hierarchy, do we automatically propane up the data which has not been requested in the hope that this will be requested data?
\item Can we understand the true need of campaign storage and understand the possible impact of the campaign storage if we run a 
hadoop-like file-system instead of a lustre/gpfs file system?
\item Can we limit the amount of data duplication? Data space is going to be very constrained on the exascale system so we must ensure that
minimal copies are made of data, and when data is duplicated, they are removed through a garbage collection routine.
\item Can we build a model to give us the time estimates during the reading and writing phases, so that rules can be in place from the user
perspective to make adaptive decisions. For example, if the file system says that reading will take 3 months, users can they place in rules to
then read in a subset of data, and they can understand which data can be read quickly and which pieces will take more time.
\item Can we understand how to place code in the system which will allow data-regeneration to take place.

>>>>

Our research into the storage system and middle ware layers must address many of these challenges including
\begin{enumerate}
\item  How do we describe the user intentions at the API layer and have this communicated down to the middle-ware and storage layers?
\item How do we allow users to define their user defined compression techniques and have this data read back from the storage system layers? Where do we execute the decompression techniques
\item How do we evaluate the tradeoffs at runtime to guide data placement, including the movement of data across the network, across the
different storage tiers? 
\item Can we use different forms of learning techniques as daemons on the system to perform data migration from one storage tier to another?
For example, if we see that a user is looking at one time slice after another for a certain object in their dataset which is in the slower tiers of 
the hierarchy, do we automatically propane up the data which has not been requested in the hope that this will be requested data?
\item Can we understand the true need of campaign storage and understand the possible impact of the campaign storage if we run a 
hadoop-like file-system instead of a lustre/gpfs file system?
\item Can we limit the amount of data duplication? Data space is going to be very constrained on the exascale system so we must ensure that
minimal copies are made of data, and when data is duplicated, they are removed through a garbage collection routine.
\item Can we build a model to give us the time estimates during the reading and writing phases, so that rules can be in place from the user
perspective to make adaptive decisions. For example, if the file system says that reading will take 3 months, users can they place in rules to
then read in a subset of data, and they can understand which data can be read quickly and which pieces will take more time.
\item Can we understand how to place code in the system which will allow data-regeneration to take place. 
\item How does the storage system do a better job in managing request from all of the users on a LCF than today? We realize that today
users who have a better middlware system can often lock other users from getting high performance when they are running. If we have 
the concept of currency which is eventually used in the same extent as node-hours, then users will have to be able to think about how much
storage and how much bandwidth they can choose. One question that needs to be understood is if there are times when the system sees
that there are very few  storage system resources being used, then the lucky users can get the bandwidth cheaper than at times of heavy usage.
How can we enforce this?
\item How do we manage all of the metdata not only from the principle objects, but from the sub-objects? How well will this scale when we have
users who can potentially create billions of objects from their simulation?
